Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
one sentence added to make it sound stronger

The primary contributions of this paper are:
\begin{itemize}
	\item An accurate motion model for pedestrian forecasting.
	\item An expedient method for computing approximations of relevant posteriors generated by our motion model.
	\item Hard error bounds on the proposed approximations.
\end{itemize}

@@

The output distributions of the three algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. 
Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
Our predictor behaves better than any of the others at moderately large $t$
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite the algorithm in \cite{Kitani2012} knowing the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.

>>>>

The primary contributions of this paper are:
\begin{itemize}
	\item An accurate motion model for pedestrian forecasting.
	\item An expedient method for computing approximations of relevant posteriors generated by our motion model.
	\item Hard error bounds on the proposed approximations.
\end{itemize}
The method proposed by this paper is able to work three times faster than the existing state of the art while improving upon its performance over long time horizons.

@@

The output distributions of the three algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. 
Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
Our predictor behaves better than any of the other compared methods at moderately large $t$.
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite providing the algorithm in \cite{Kitani2012} with the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.
